Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-05-05 introduction/Subsections/Motivation.tex
Updates from Overleaf

>>>>

%%%%%%%% PERCEPTION %%%%%%%%%%%%%

Kurt Koffka (1886-1941) was a German psychologist and a founding member of the Gestalt school of psychology, along with Max Wertheimer and Wolfgang Köhler. Gestalt psychology emerged as a reaction against the structuralist approach to psychology, emphasizing analyzing mental processes into their most basic elements. Instead, Gestalt psychologists sought to understand the principles underlying the organization and perception of complex forms and wholes.

Koffka's most significant contribution to the field was the development of the principles of Gestalt psychology and their application to perception. His 1935 book, ``Principles of Gestalt Psychology,'' remains a seminal work in the field \cite{Koffka2013PrinciplesPsychology}. In it, Koffka systematically describes the foundational concepts of Gestalt psychology and presents empirical evidence to support these ideas.

Applying the principles of Gestalt psychology to music can provide valuable insights into the cognitive processes underlying musical perception, organization, and interpretation. In music, just as in visual perception, the human mind seeks to identify patterns and structures to make sense of the auditory input. Several Gestalt principles can be applied to understanding musical perception, such as the law of Prägnanz, grouping principles, and holistic processing.

As with visual perception, the mind organizes musical information into the most straightforward and stable patterns. This principle can be observed in listeners' perceptions of harmony, melody, and rhythm. For example, Western tonal music is built upon hierarchical structures that allow the listener to make sense of complex musical information by organizing it coherently \cite{Lerdahl1985AMusic}.

In conclusion, applying the principles of Gestalt psychology to the study of music has led to a deeper understanding of the cognitive processes underlying musical perception and organization. This approach has influenced various areas of music research, including music theory, music cognition, and music therapy.
